\documentclass[a4paper]{article}
\usepackage{xeCJK}
\usepackage{geometry}
\usepackage[colorlinks,linkcolor=blue]{hyperref}
\newcommand\email[1]{\href{mailto:#1}{\uline{\nolinkurl{#1}}}}
\geometry{left=2.5cm,right=2.5cm,top=2.5cm,bottom=4cm}
\title{English Homework}
\author{Reggie \\Xiaoling Long\\Student ID.:81943968\\Email:\email{longxl@shanghaitech.edu.cn}}
\usepackage{graphicx}
\usepackage{amsmath, amsthm, amssymb}
%\usepackage{subfloat}
\newtheorem{prop}{Proposition}
\usepackage{ulem}
%\usepackage{indentfirst}
\begin{document}
\maketitle
\begin{description}
  \item[Ethics 1]Wife or mom, who would you choose?
  \item[Answer 1]
    Maybe I will save the closest one to me. In the class, I get 5 points of Daoism and 5 points are the highest score I get.
    I totally agree some principle in Daoism. The idea of Daoism is doing nothing and nature. But I agree with the thought about nature
    about not in doing nothing. I think everything has the sake for existing in this world.
    But I also get 4 points Utilitarian. So I will do some judge this two result and combine my own situation.
    I am not good at swimming and if there isn't any special situation such as that my wife is pregnant or my mother has lot of money :P.
    So, I will save the closed one to me without special situation or some important sake will change me. I hope there is not some strange condition.
  \item[Ethics 2]Kill one starnger or let 5 strangers die?
  \item[Answer 2]Maybe I will let 5 strangers die and just pretend dozing off. Just as the first question,
  I agree with part of Daosim and Utilitarian. So I don't know why they are there, and I don't want to know the story behind. I just know
  I am the driver of this train. And my job is to drive this train to the desired destination. So my most nature thing
  is keep train safe. And I don't know these guys. And I don't know wether they are useful to me
  so I will do something just like Daoism. I will do nothing. But I will pretend dozing off. But actually if I know one of these
  guys, I will think about it wether he is useful to me or helped me before. But they are just strangers :).
\end{description}
\end{document}
